A Taxonomy of Twists of Supersymmetric Yang--Mills Theory

### 2020-02-13 paper.tex
Brian's many papers
reconciling

 \caption{Twists of Maximally Supersymmetric Pure Yang-Mills Theories with gauge Lie algebra $\fg$ (16 supercharges).}

@@

It will be convenient for us to represent spaces of fields in classical field theories in terms of mapping spaces. In this section we explain their meaning, while in the rest of the paper it will be just a convenient notation.

@@

\begin{prop}
Consider $X,Y,M, \fg$ as in Example \ref{ex:mappingspace}. The local formal moduli problem $T^*[n]\map(X\times Y_{\mathrm{Dol}}\times M_{\mathrm{dR}}, B\fg)$ is isomorphic to the local formal moduli problem
\[\Sect\left(X\times Y_{\mathrm{Dol}}\times M_{\mathrm{dR}}, T^*[n+\dim(X)+2\dim(Y)+\dim(M)] B\fg\times_{\Gm} (K_X\otimes \Dens_M)\right),\]
where $K_X$ is the canonical bundle of $X$ and $\Dens_M$ is the line bundle of densities on $M$.
\end{prop}
\begin{proof}
The claim follows from the following isomorphisms of graded vector bundles:
\begin{align*}
\left(\Omega^{0, \bullet}_X\right)^!&\cong \Omega^{0, \bullet}_X\otimes K_X[\dim(X)] \\
\left(\Omega^{\bullet, \bullet}_Y\right)^!&\cong \Omega^{\bullet, \bullet}_Y[2\dim(Y)] \\
\left(\Omega^\bullet_M\right)^!&\cong \Omega^\bullet_M\otimes \Dens_M[\dim(M)].
\end{align*}
\end{proof}

@@

\item The pairing
\begin{align*}
\cL_c\otimes \cL_c&\rightarrow \CC \\
\alpha\otimes \beta&\mapsto \int_M \langle \alpha, \beta\rangle
\end{align*}
is an invariant pairing on the $L_\infty$ algebra $\cL_c$.
\end{enumerate}
\end{definition}

@@

Given a classical field theory represented by a local $L_\infty$ algebra $L$ on $M$, we call $E=L[1]$ the \defterm{bundle of BV fields}. Moreover, we call the Poisson bracket on $\oloc(\cM)$ the \defterm{BV bracket}. It will be convenient to think of a classical field theory as a triple $(E, \omega, S)$ of the bundle of BV fields equipped with a $(-1)$-shifted symplectic pairing $\omega$ and an action functional $S$.

\begin{example}
Let $\cM=BL$ be a local formal moduli problem. Then the $(-1)$-shifted cotangent bundle $T^*[-1]\cM$ carries a natural $(-1)$-shifted symplectic structure. Indeed, $T^*[-1]\cM = B(L\oplus L^![-3])$ and we simply pair $L$ and $L^!$. Classical field theories arising via this construction are called of \defterm{cotangent type}.
\end{example}

%The classical BV (Batalin-Vilkovisky) formalism \cite{BatalinVilkovisky} is a model for classical field theory from the Lagrangian perspective.  In brief the classical BV formalism produces a local model for the critical locus of an action functional, but considered in the derived sense.  That is, given a space $\Phi$ of fields and an action functional with derivative $\d S$, one considers not just the usual locus in $\Phi$ of fields with $\d S(\phi) = 0$, but the derived intersection $\mr{dCrit}(S) = \Phi \cap^h_{T^*\Phi} \Gamma_{\d S}$ of the zero section in $T^*\Phi$ with the graph of $\d S$.  The formalism we describe below can be interpreted as an abstract formalism for modelling the tangent complex at a point to a derived critical locus $\mr{dCrit}(S)$.

@@

Besides the $\ZZ$-graded classical field theories defined above, we may consider the following variants of the above definition:
\begin{itemize}
\item A $\ZZ\times \ZZ/2\ZZ$-graded local $L_\infty$ algebra is a $\ZZ$-graded local $L_\infty$ algebra $L$ equipped with an extra $\ZZ/2\ZZ$-grading (the \defterm{fermionic grading}) with respect to which all operations are even. An $n$-shifted symplectic structure on a $\ZZ\times\ZZ/2\ZZ$-graded local formal moduli problem $BL$ is a pairing $L\otimes L\rightarrow \Dens_M[n-2]$ which is even with respect to the fermionic grading.

\item A $\ZZ/2\ZZ$-graded classical field theory is defined in the same way as a $\ZZ$-graded classical field theory where we only consider the cohomological grading modulo 2.
\end{itemize}

@@

% \begin{prop}
% Suppose $(E, Q_{\mr{BV}}, \omega, I)$ is a classical field theory, $F\rightarrow M$ is a graded vector bundle, such that $E\cong E_0\oplus E_1\oplus E_1^![-1]\oplus E_1^!\oplus E_1[-1]$. Denote by $\phi, \phi^*$ sections of $E_1,E_1^![-1]$ and by $\psi, \psi^*$ sections of $E_1^!, E_1[-1]$. Suppose
% \[Q_{\mr{BV}}\phi + \{I, \phi\} = \phi - f_\psi \in E_1[-1] ,\qquad Q\psi + \{I, \psi\} = \psi - f_{\phi} \in E_1^![-1],\]
% where $f_\phi$ is independent of $\psi$ and $f_{\psi}$ is independent of $\phi$. Then the theory $(E, Q_{\mr{BV}}, \omega, I)$ is perturbatively equivalent to the theory $(E_0, Q_0, \omega_0, I_0)$ with the BV action obtained by setting $\phi = f_\psi, \phi^* = 0,  \psi = f_\phi, \psi^* = 0$ in the original BV action.
% \end{prop}

@@

%The operator $Q_{\mr{BV}}$ on $\oloc(\cE)$ extends $C^\bu(\fg)$-linearly to an operator on $C^\bullet(\fg, \oloc(\cE))$ by the rule
%\[
%(Q_{\mr{BV}} f)(x_1,\ldots, x_n) = Q_{\mr{BV}} f(x_1,\ldots, x_n) 
%\]
%where $f \colon \fg^{\otimes n} \to \oloc(\cE)$. 
%The differentials $\d_{\mr{CE}}$ and $Q_{\mr{BV}}$ are compatible in the sense that $(\d_{\mr{CE}} + Q_{\mr{BV}})^2 = 0$ making $C^\bu(\fg, \oloc(\cE))$ into a cochain complex with total differential $\d_{\mr{CE}} + Q_{\mr{BV}}$. 
%Via the BV bracket, the shift of this cochain complex $C^\bu(\fg, \oloc(\cE))[-1]$ is a dg Lie algebra.  This shifted cotangent complex will model equivariant local observables in our classical field theory, but to finish defining the $\gg$ action we must define the equivariant version of the classical interaction.  This is defined as follows.

@@

@@

@@

@@

%\begin{example}
%There is a special case of this, which one might label the ``holomorphic symplectic boson'' \cite[Definition 4.8]{SWchar}.  This is the case when $n_1 = 1$, $n_2 = n_3 = 0$, so $V$ is a $\fg$ representation with an ordinary symplectic structure.  If $V = T^*R$, we are considering the classical cotangent field theory whose classical solutions to the equations of motion model the cotangent bundle to $G$-bundles on a Riemann surface with a section of the associated bundle to $R$.
%\end{example}

@@

The BV theory of supersymmetric Yang-Mills is the BV theory associated to this BRST theory. 
By definition, the fields are identified with sections of the bundle $T^*[-1] F_{\rm gauge} = F_{\rm gauge} \oplus F_{\rm gauge}^! [-1]$. 
If we denote by $(A^*, \lambda^*,c^*)$ the anti-fields, the full BV action takes the form:
%We introduce gauge transformations
%\[\delta A = -\d_A c,\qquad \delta \lambda = [c, \lambda],\qquad \delta c = \frac{1}{2}[c, c],\]
%so that the BV action is given by
\begin{equation}
S_{\gauge} = \int_{V_\RR}\dvol \left( -\frac{1}{4} (F_A, F_A) + \frac{1}{2}(\lambda, \sd\d_A \lambda) + (\d_A c, A^*) + ([c, \lambda], \lambda^*) + \frac{1}{2}([c, c], c^*)\right).
\label{eq:YMBVaction}
\end{equation}
%
%We also introduce their antifields $A^*\in\Omega^1(V_\RR; \fg[-1])$, $\lambda^*\in\Gamma(V_\RR; \Pi\Sigma^*\otimes \fg[-1])$ and $c^*\in\Gamma(V_\RR; \fg[-2])$. Let $\cE_{\gauge}$ denote the space of BV fields. 
To simplify the notation, the pairing on $\fg$ from now on will be implicit.

@@

%The R-symmetry group is $\spin(2;\CC) = \CC^\times$, acting on $W$ by its defining representation.

@@

\begin{proof}
Let $W_4$ be the complex two-dimensional auxiliary space of the 4d $\cN=2$ supesymmetry algebra.
The projection from the 4d $\mc N=2$ supertranslation algebra to the 3d $\mc N=4$ supertranslation algebra induces an isomorphism $W_4 \oplus W_4^* \to W$ of representations of the group $\spin(3;\CC)$.  
This splits the fundamental representation $W$ into the sum of two Lagrangians, defining an orientation on $W$. 
A rank $(2,0)$ supercharge induces the Lagrangian subspace $W_4 \sub W$, which is oriented.  The corresponding twist can be promoted to a twisting datum using a copy of $\mr U(1)$ acting with weight 1 on $W_4$; explicitly, this is the homomorphism $\alpha : \U(1) \to G_R = \SL(2;\CC) \times \SL(2;\CC)$ given by the embedding into the second factor. 
This is the $A$-twist in our classification above.
%-- if $G_R = \SL(2;\CC)_+ \times \SL(2;\CC)_-$ where the first factor is the 4d R-symmetry group, by a $\mr U(1)$ in the second factor -- so this is the A-twist in our classification above.

@@

% \cN=(0,8) Super Yang-Mills with matter

>>>>

 \caption{Twists of Maximally Supersymmetric Pure Yang-Mills Theories with Lie algebra $\fg$ (16 supercharges).}

@@

The classical BV (Batalin-Vilkovisky) formalism \cite{BatalinVilkovisky} is a model for classical field theory from the Lagrangian perspective.  In brief, the classical BV formalism produces a local model for the critical locus of an action functional, but considered in the derived sense.  That is, given a space $\mc F$ of fields and an action functional with derivative $\d S$, one considers not just the usual locus in $\mc F$ of fields with $\d S(\phi) = 0$, but the derived intersection $\mr{dCrit}(S) = \mc F \cap^h_{T^*\mc F} \Gamma_{\d S}$ of the zero section in $T^*\mc F$ with the graph of $\d S$.  The formalism we describe below can be interpreted as an abstract formalism for modelling the tangent complex at a point to a derived critical locus $\mr{dCrit}(S)$ as a formal moduli problem.

@@

\begin{prop}
Consider $X,Y,M, \fg$ as in Example \ref{ex:mappingspace}. The local formal moduli problem $T^*[n]\map(X\times Y_{\mathrm{Dol}}\times M_{\mathrm{dR}}, B\fg)$ is isomorphic to the local formal moduli problem
\[\Sect\left(X\times Y_{\mathrm{Dol}}\times M_{\mathrm{dR}}, T^*[n+\dim(X)+2\dim(Y)+\dim(M)] B\fg\times_{\Gm} (K_X\otimes \Dens_M)\right),\]
where $K_X$ is the canonical bundle of $X$ and $\Dens_M$ is the line bundle of densities on $M$.
\label{prop:mapintocotangent}
\end{prop}
\begin{proof}
The claim follows from the following isomorphisms of graded vector bundles:
\begin{align*}
\left(\Omega^{0, \bullet}_X\right)^!&\cong \Omega^{0, \bullet}_X\otimes K_X[\dim(X)] \\
\left(\Omega^{\bullet, \bullet}_Y\right)^!&\cong \Omega^{\bullet, \bullet}_Y[2\dim(Y)] \\
\left(\Omega^\bullet_M\right)^!&\cong \Omega^\bullet_M\otimes \Dens_M[\dim(M)].
\end{align*}
\end{proof}

@@

\item The pairing $\cL_c\otimes \cL_c \rightarrow \CC$ defined by
\[\alpha\otimes \beta \mapsto \int_M \omega( \alpha, \beta)\]
is an invariant pairing on the $L_\infty$ algebra $\cL_c$.
\end{enumerate}
\end{definition}

@@

Given a classical field theory represented by a local $L_\infty$ algebra $L$ on $M$, we call $E=L[1]$ the \defterm{bundle of BV fields}, and we call the complex $(E, Q_{\mr{BV}})$ the \defterm{classical BV complex}. We call the Poisson bracket on $\oloc(\cM)$ the \defterm{BV bracket}. It will be convenient to think of a classical field theory as a quadruple $(E, \omega, Q_{\mr{BV}}, I)$ consisting of the bundle of BV fields equipped with a $(-1)$-shifted symplectic pairing $\omega$, a classical BV differential $Q_{\mr{BV}}$ and an interaction functional $I$.  We characterize such data in the following way.

\begin{definition}
A \defterm{free BV theory} on a manifold $M$ is the data of:
\begin{itemize}
\item a finite rank graded vector bundle $E \to M$ equipped with an even differential operator of cohomological degree $+1$
\[
Q_{\mr{BV}} \colon \cE \to \cE [1] 
\]
such that $(1)$: $Q_{\mr{BV}}^2 = 0$ and $(2)$: the pair $(\cE , Q_{\mr{BV}})$ is an elliptic complex;
\item a map of bundles
\[
\omega\colon E \otimes E \to \Dens_M [-1]
\]
that is
\begin{enumerate}
\item[$(1)$] fiberwise nondegenerate,
\item[$(2)$] graded skew symmetric, and
\item[$(3)$] satisfies $\int_M \omega(e_0, Q_{\mr{BV}} e_1) = (-1)^{|e_0|} \int_M \omega(Q_{\mr{BV}} e_0, e_1)$ where $e_i$ are compactly supported sections of $E$ .
\end{enumerate}
\end{itemize}
\end{definition}

The datum of a classical BV field theory as in Definition \ref{def:classicalfieldtheory} is equivalent to the datum of a free BV theory $(E, Q, \omega)$ equipped with an even functional
\[I \in \oloc^+(\cE)\]
of cohomological degree zero satisfying the Maurer-Cartan equation
\[Q_{\mr{BV}} I + \frac{1}{2} \{I,I\} = 0,\]
under the identification of the BV action as
\[S = \frac{1}{2} \int_M \omega(e, Q_{\mr{BV}} e) + I\in \oloc(E).\]

\begin{example} \label{def:cotangent_type}
Let $\cM=BL$ be a local formal moduli problem. Then the $(-1)$-shifted cotangent bundle $T^*[-1]\cM$ carries a natural $(-1)$-shifted symplectic structure. Indeed, $T^*[-1]\cM = B(L\oplus L^![-3])$ and we simply pair $L$ and $L^!$. Classical field theories arising via this construction are called of \defterm{cotangent type}.
\end{example}

@@

\begin{remark}
Besides the $\ZZ$-graded classical field theories defined above, we may consider the following variants of the above definition:
\begin{itemize}
\item A $\ZZ\times \ZZ/2\ZZ$-graded local $L_\infty$ algebra is a $\ZZ$-graded local $L_\infty$ algebra $L$ equipped with an extra $\ZZ/2\ZZ$-grading (the \defterm{fermionic grading}) with respect to which all operations are even. An $n$-shifted symplectic structure on a $\ZZ\times\ZZ/2\ZZ$-graded local formal moduli problem $BL$ is a pairing $L\otimes L\rightarrow \Dens_M[n-2]$ which is even with respect to the fermionic grading.

\item A $\ZZ/2\ZZ$-graded classical field theory is defined in the same way as a $\ZZ$-graded classical field theory where we only consider the cohomological grading modulo 2.
\end{itemize}
\end{remark}

@@

@@

The operator $Q_{\mr{BV}}$ on $\oloc(\cE)$ extends $C^\bu(\fg)$-linearly to an operator on $C^\bullet(\fg, \oloc(\cE))$ by the rule
\[
(Q_{\mr{BV}} f)(x_1,\ldots, x_n) = Q_{\mr{BV}} f(x_1,\ldots, x_n) 
\]
where $f \colon \fg^{\otimes n} \to \oloc(\cE)$. 
The differentials $\d_{\mr{CE}}$ and $Q_{\mr{BV}}$ are compatible in the sense that $(\d_{\mr{CE}} + Q_{\mr{BV}})^2 = 0$ making $C^\bu(\fg, \oloc(\cE))$ into a cochain complex with total differential $\d_{\mr{CE}} + Q_{\mr{BV}}$. 
Via the BV bracket, the shift of this cochain complex $C^\bu(\fg, \oloc(\cE))[-1]$ is a dg Lie algebra.  This shifted cotangent complex will model equivariant local observables in our classical field theory, but to finish defining the $\gg$ action we must define the equivariant version of the classical interaction.  This is defined as follows.

@@

\begin{remark}
We have seen that a classical BV theory can also be presented in terms of a BV differential $Q_{\mr{BV}}$ and an interaction $I$ satisfying the Maurer-Cartan equation
\[Q_{\mr{BV}} I + \frac{1}{2} \{I,I\} = 0 .\]
One can also formulate actions of a Lie algebra on a classical theory in these terms. 
The data of an action of a Lie algebra $\fg$ on a classical field theory $(E, \omega, S)$ is equivalent to the choice of a local interaction functional 
\[I_\fg = \sum_{k\geq 0} I_{\fg}^{(k)} \text{ in } C^\bullet(\fg, \oloc(\cE)),\]
satisfying the Maurer-Cartan equation
\[(\d_{\mr{CE}} + Q_{\mr{BV}}) I_\fg + \frac{1}{2} \{I_\fg, I_\fg\} = 0.\]
\end{remark}

@@

In the case where $S_{\mr{BRST}} = 0$, the associated BV theory is of cotangent type, as in Example \ref{def:cotangent_type}.

\begin{remark}
In general, multiple BRST theories can give rise to the same BV theory.  A BV theory $(E, Q_{\mr{BV}}, \omega, I)$ is of cotangent type as long as there is \emph{some} $F$ with $S_{\mr{BRST}} = 0$ producing the given theory using the construction above.  Theories of cotangent type can still have interesting, non-trivial action functionals, encoded by the $L_\infty$ structure on $F$.
\end{remark}

@@

\begin{example}
There is a special case of this, which one might label the ``holomorphic symplectic boson'' \cite[Definition 4.8]{SWSuperconformal} which is the theory
\[\Sect(\CC, (U\otimes K_\CC^{1/2})\ham\fg).\]
For $U=T^*R$ this theory is isomorphic to the holomorphic BF theory
\[T^*[-1] \map(\CC, R / \fg)\]
by Proposition \ref{prop:mapintocotangent}.
\end{example}

@@

@@

The BV theory of supersymmetric Yang-Mills is the BV theory associated to this BRST theory. 
By definition, the fields are identified with sections of the bundle $T^*[-1] F_{\rm gauge} = F_{\rm gauge} \oplus F_{\rm gauge}^! [-1]$. 
If we denote by $(A^*, \lambda^*,c^*)$ the anti-fields, the full BV action takes the form:
%We introduce gauge transformations
%\[\delta A = -\d_A c,\qquad \delta \lambda = [c, \lambda],\qquad \delta c = \frac{1}{2}[c, c],\]
%so that the BV action is given by
\begin{equation}
S_{\gauge} = \int_{V_\RR}\dvol \left( -\frac{1}{4} (F_A, F_A) + \frac{1}{2}(\lambda, \sd\d_A \lambda) + (\d_A c, A^*) + ([c, \lambda], \lambda^*) + \frac{1}{2}([c, c], c^*)\right).
\label{eq:YMBVaction}
\end{equation}

To simplify the notation, the pairing on $\fg$ from now on will be implicit.

@@

@@

\begin{proof}
Let $W_4$ be the complex two-dimensional auxiliary space of the 4d $\cN=2$ supesymmetry algebra.
The projection from the 4d $\mc N=2$ supertranslation algebra to the 3d $\mc N=4$ supertranslation algebra induces an isomorphism $W_4 \oplus W_4^* \to W$ of representations of the group $\spin(3;\CC)$.  
This splits the fundamental representation $W$ into the sum of two Lagrangians, defining an orientation on $W$. 
A rank $(2,0)$ supercharge induces the Lagrangian subspace $W_4 \sub W$, which is oriented.  The corresponding twist can be promoted to a twisting datum using a copy of $\mr U(1)$ acting with weight 1 on $W_4$; explicitly, this is the homomorphism $\alpha : \U(1) \to G_R = \SL(2;\CC) \times \SL(2;\CC)$ given by the embedding into the second factor. 
This is the $A$-twist in our classification above.

@@
